---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(dplyr)
library(tidyr)
library(readr)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw_messy <- read_csv("../data/raw/data_demographics_raw_messy.csv", skip = 2) |>
  janitor::clean_names()

data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

Clean the demographics data so that summaries of age and gender can be made in the analysis.

```{r}

 dat_age_gender <- data_demographics_raw %>% 
   rename(unique_id = subject, item = trialcode) %>% 
   select(unique_id, item, response)

temp <- dat_age_gender %>% 
  filter(item == "age")

temp2 <- dat_age_gender %>% 
  filter(item == "age") %>% 
mutate(response = str_remove_all(response, "\\D"),
         response = na_if(response, "")
       )
colnames(temp2)
colnames(temp3)

temp3 <- dat_age_gender %>% 
 filter(item == "gender") %>% 
#put everything into lowercase letters
  mutate(response = if_else(item == "gender", tolower(response), response)) %>%
  # Standardize 'response' for gender to "female", "male" or "non binary"
  mutate(response = case_when( 
    #unify all variations to "female"
    item == "gender" & response %in% c("female", "f") ~ "female",  
    #unify all variations to "male"
    item == "gender" & response %in% c("male", "m") ~ "male",
    #unify all variations to "non binary"
    item == "gender" & response %in% c("non binary", "non-binary", "nb") ~ "non binary", 
    #set all responses that werent covered in the code above to "NA"
    item == "gender" ~ NA_character_, 
    # Keep other responses unchanged (like age)
    TRUE ~ response  
  ))

# Assuming temp2 has cleaned age data and temp3 has cleaned gender data
combined_data <- bind_rows(temp2, temp3)
# Pivot the combined data to have separate 'age' and 'gender' columns
final_data1 <- combined_data %>%
  #pivot the format from item and response to age and gender
  pivot_wider(names_from = item, values_from = response)
library("purrr")
final_data2 <- final_data1 %>% 
  #remove all non-unique entries
  mutate(
    age = map_chr(age, ~ ifelse(length(unique(.x)) == 1, unique(.x)[1], NA_character_)),
    gender = map_chr(gender, ~ ifelse(length(unique(.x)) == 1, unique(.x)[1], NA_character_))
  )

final_data3 <- final_data2 %>% 
  mutate(age = as.numeric(age))
  

library(ggplot2)

# Boxplot to show age distribution and outliers
ggplot(final_data3, aes(y = age)) +
  geom_boxplot() +
  labs(title = "Distribution of Ages with Outliers", y = "Age") +
  theme_minimal()

# Histogram to show distribution of age
ggplot(final_data3, aes(x = age)) +
  geom_histogram(binwidth = 5, fill = "blue", color = "black") +
  labs(title = "Age Distribution", x = "Age", y = "Count") +
  theme_minimal()

# Summary statistics for age
summary_stats <- final_data3 %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    sd_age = sd(age, na.rm = TRUE),
    min_age = min(age, na.rm = TRUE),
    max_age = max(age, na.rm = TRUE)
  )

summary_stats


```

# Exclusions / data quality

## AMP

Create an exclusion variable `exclude_amp_performance` based on AMP performance: "exclude" if more than 10% of trials are < 100ms, or "include" if not.

Create an exclusion variable `exclude_amp_completeness` based on the AMP having the right number of trials.

```{r}

#data_amp_performance_criteria <- data_amp_raw 

```

# Self-reports

Create a mean score for each participant of the three self-report items.

```{r}

#data_selfreport_trial_level <- data_selfreport_raw 

```

# Affect Misattribution Procedure

Create an overall AMP bias score. Score each trial as having been evalauted as congruent with the prime or not. eg When trialcode == "prime_positive" & evaluative_response == 1, then record as 1, etc. AMP score is the proportion of congruent responses.

```{r}

#data_amp_score_congruence <- data_amp_raw 

```

# Combine 

Combine data frames together to create one wide-format data frame where each row represents a participant.

Flag all duplicates for exclusion.

```{r}

# data_processed_before_exclusions 

```

# Define master exclusion variable

```{r}

#data_processed <- data_processed_before_exclusions

```

# Write to disk

```{r}

# # in case this dir doesn't exist, create it
# dir.create("../data/processed/")
# 
# # save data to disk in that dir
# write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


